\begin{abstract}
Graphical user interface (GUI) grounding is a key capability for computer-use agents, mapping natural-language instructions to actionable regions on the screen. Existing Multimodal Large Language Model (MLLM) approaches typically formulate GUI grounding as a text-based coordinate generation task. However, directly generating precise coordinates from visual inputs is challenging and often data-intensive.
A more intuitive strategy is to first \textit{identify instruction-relevant visual patches and then determine the exact click location within them}.
Motivated by recent observations that general MLLMs exhibit native grounding ability embedded in their attention maps,
we propose \method{},
an attention-based and coordinate-free supervised fine-tuning framework for efficient GUI grounding.
\method{} aligns the intrinsic multimodal attention of MLLMs with patch-wise grounding signals. These signals are calculated adaptively for diverse user instructions by multi-head aggregation on simplified query-visual attention matrices. Besides, its coordinate-free manner can easily integrate a plug-and-play zoom-in stage. \method{}-3B was trained with only 509k samples ($\sim$101k screenshots), demonstrating exceptional data efficiency and verifying that light training can trigger the native grounding capability of MLLMs. It achieves state-of-the-art performance among 3B models, attaining an average accuracy of \textbf{61.5\%} on ScreenSpot-Pro, \textbf{92.1\%} on ScreenSpot-v2, \textbf{68.1\%} on OSWorld-G, \textbf{79.1\%} on MMBench-GUI-L2 and \textbf{60.0\%} on UI-Vision.
Project page: \url{https://github.com/sjz5202/GUI-AIMA}.
\end{abstract}